Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-12-18 manuscript/appendix.Rmd
corrected p <= 0.05

\blandscape
## Figure S4. Individual plots of forest C fluxes in relation to mean annual climate, part 1
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of forest C fluxes in relation to mean annual climate, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

\newpage
## Figure S5. Individual plots of forest C fluxes in relation to mean annual climate, part 2
```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of forest C fluxes in relation to mean annual climate, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

## Figure S6. Individual plots of forest C fluxes in relation to mean climate seasonality, part 1
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of forest C fluxes in relation to mean climate seasonality, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height ='80%', fig.pos='H'}

@@

\newpage
## Figure S7. Individual plots of forest C fluxes in relation to mean climate seasonality, part 2
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of forest C fluxes in relation to mean climate seasonality, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.width ='80%', fig.pos='H'}

@@

\newpage
## Figure S8. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}

@@

\newpage
## Figure S9. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}

>>>>

\blandscape
## Figure S4. Individual plots of forest C fluxes in relation to mean annual climate, part 1
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of forest C fluxes in relation to mean annual climate, part 1. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

\newpage
## Figure S5. Individual plots of forest C fluxes in relation to mean annual climate, part 2
```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of forest C fluxes in relation to mean annual climate, part 2. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

## Figure S6. Individual plots of forest C fluxes in relation to mean climate seasonality, part 1
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of forest C fluxes in relation to mean climate seasonality, part 1. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height ='80%', fig.pos='H'}

@@

\newpage
## Figure S7. Individual plots of forest C fluxes in relation to mean climate seasonality, part 2
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of forest C fluxes in relation to mean climate seasonality, part 2. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.width ='80%', fig.pos='H'}

@@

\newpage
## Figure S8. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}

@@

\newpage
## Figure S9. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2. Statistical signficance is indicated by solid (p $\\le$ 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}
